Amazonian Narratives in Presidential Discourse (1985 to 2020)

### 2022-01-27 11112021_Sposito_and_SilvaMuller_DRAFT.Rmd
#olduncommittedchanges

---
title: "Amazonian Narratives in Presidential Discourse (1985 to 2020)"
author:
- Henrique Sposito^[Phd Candidate, The Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
- Livio Silva-Muller^[Phd Candidate, The Graduate Institute Geneva, livio.silva@graduateinstitute.ch]
date: "11/11/2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

@@

freq_year <- dplyr::left_join(freq_year, amazon_def_year, by = "year") 
ggplot(freq_year, aes(x = year)) +
    geom_line(aes(y = freqn, color = "Frequency of amazonian speeches")) +
    geom_line(aes(y = `area km²`/100, color = "Annual deforestation (km²/100)")) +
      labs(x = "",
       y = "Relative share of speeches per year",
       title = "Presidential Speeches mentioning the Amazon (1985-2020)",
       subtitle = "Compared to annual deforestation rates since 1988",
       color = "")+
       theme(legend.position ="bottom")

@@

  The summary table illustrates that more speeches that mention the Amazon proportionally take place in Amazonian states in comparison to their proportion in all speeches. However, when it comes to international settings, a lower proportion of the speeches that mention the Amazon take place in international settings in comparison to all speeches. We find this counter-intuitive, as many scholars tend to associate Brazil's prominent role in international environmental governance. At the moment, we still can not say for sure that this finding is robust. We operationalize international stage as anything that is not Brazil, so it includes speeches in African countries for instance. We will work towards a better measure that separates international stage from other countries and re-run this to see if it still holds.

@@

# Let's see if bigrams help us more here
tamazon <- tidytext::tidy(amazon_corpus) %>%
  unnest_tokens(bigram, text , token = "ngrams", n = 2) %>%
  dplyr::count(bigram, sort = TRUE) %>%
  ungroup()

@@

  The table 2 (above) and table 4(below) portray the result of a structural topic model. We utilize LDA (Latent Dirichlet allocation), which is a model for estimating the mixture of words associated with a topic (cluster) and determining the probabilities of topics in each mention, we start to see some interesting patterns (for more information on LDA and R approaches [here](https://www.tidytextmining.com/index.html)). We set the number of clusters to be found (topics) at 10, randomly. We, then, select the top ten words coded for each topic.

@@

# Visualize correlations
am_narratives <- Amazon_speeches %>%
  dplyr::select(-c(context, text, fulltext, president, party, date, title, doc_id, location)) %>%
  tidyr::pivot_longer(sovereignty:other) %>% 
  group_by(year, name) %>% 
  summarise(value = sum(value)) %>% 
  rename(narrative = name)

ggplot(am_narratives, aes(x = year, y = value , fill = narrative)) +
  geom_line(aes(group = narrative, color = narrative), size = 1) +
  labs(x = "Year",
       y = "",
       title = "Narratives in Presidential Speeches per year since 1985 in Brazil")+
    geom_smooth(method=lm, se=FALSE, color="black", linetype="dashed",size=0.5)+
    facet_wrap(~narrative)+
    theme (legend.position="none")

>>>>

---
title: "Amazonian Narratives in Presidential Discourse (1985 to 2020)"
author:
- Henrique Sposito^[Phd Candidate, The Graduate Institute Geneva, henrique.sposito@graduateinstitute.ch]
- Livio Silva-Muller^[Phd Candidate, The Graduate Institute Geneva, livio.silva@graduateinstitute.ch]
date: "11/11/2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

@@

cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

freq_year <- dplyr::left_join(freq_year, amazon_def_year, by = "year") 
ggplot(freq_year, aes(x = year)) +
    geom_line(aes(y = freqn, color = "Frequency of amazonian speeches")) +
    geom_line(aes(y = `area km²`/100, color = "Annual deforestation (km²/100)")) +
      labs(x = "",
       y = "Relative share of speeches per year",
       title = "Presidential Speeches mentioning the Amazon (1985-2020)",
       subtitle = "Compared to annual deforestation rates since 1988",
       color = "")+
       theme(legend.position ="bottom")+
        scale_colour_manual(values=cbbPalette)

@@

 Table 1 illustrates that more speeches that mention the Amazon proportionally take place in Amazonian states in comparison to their proportion in all speeches. However, when it comes to international settings, a lower proportion of the speeches that mention the Amazon take place in international settings in comparison to all speeches. We find this counter-intuitive, as many scholars tend to associate Brazil's prominent role in international environmental governance. At the moment, we still can not say for sure that this finding is robust. We operationalize international stage as anything that is not Brazil, so it includes speeches in African countries for instance. We will work towards a better measure that separates international stage from other countries and re-run this to see if it still holds.

@@

# Let's see if bigrams help us more here
tamazon <- tidytext::tidy(amazon_corpus) %>%
  unnest_tokens(bigram, text , token = "ngrams", n = 2) %>%
  dplyr::count(bigram, sort = TRUE) %>%
  ungroup()
tamazon

@@

  The table 3 (above) and table 4(below) portray the result of a structural topic model. We utilize LDA (Latent Dirichlet allocation), which is a model for estimating the mixture of words associated with a topic (cluster) and determining the probabilities of topics in each mention, we start to see some interesting patterns (for more information on LDA and R approaches [here](https://www.tidytextmining.com/index.html)). We set the number of clusters to be found (topics) at 10, randomly. We, then, select the top ten words coded for each topic.

@@

# Visualize correlations

cbPalette <- c("#999999", "#56B4E9", "#0072B2", "#009E73", "#F0E442", "#D55E00", "#CC79A7", "#E69F00")

am_narratives <- Amazon_speeches %>%
  dplyr::select(-c(context, text, fulltext, president, party, date, title, doc_id, location)) %>%
  tidyr::pivot_longer(sovereignty:other) %>% 
  group_by(year, name) %>% 
  summarise(value = sum(value)) %>% 
  rename(narrative = name)

ggplot(am_narratives, aes(x = year, y = value , fill = narrative)) +
  geom_line(aes(group = narrative, color = narrative), size = 1) +
  labs(x = "Year",
       y = "",
       title = "Narratives in Presidential Speeches per year since 1985 in Brazil (wrapped)")+
    geom_smooth(method=lm, se=FALSE, color="black", linetype="dashed",size=0.5)+
    facet_wrap(~narrative)+
    theme (legend.position="none")+
    scale_colour_manual(values=cbPalette)

ggplot(am_narratives, aes(x = year, y = value , fill = narrative)) +
  geom_line(aes(group = narrative, color = narrative), size = 1) +
  labs(x = "Year",
       y = "",
       title = "Narratives in Presidential Speeches per year since 1985 in Brazil")+
    theme (legend.position="bottom")+
    scale_colour_manual(values=cbPalette)
